Reply To Examiners

### 2014-06-04 answer_thesis_examiner/chap1.tex

\rowcolors{2}{gray!25}{white}    
\noindent
\begin{longtable}[c]{p{0.08\textwidth}|p{0.08\textwidth}|p{0.36\textwidth}|p{0.36\textwidth}}
\textbf{Page} & \textbf{Line} & \textbf{Gramatical Errors} & \textbf{Corrections} \\
 \hline
\endhead
4 & 5 & missing references & citation added \\
4 & 8 & missing references & citation added \\
5 & 13 & techniques ... has & techniques ... have \\
6 & 5 & many fold & manyfold \\
14 & 5 & Assuming the number of these elementary back scatterers is sufficiently large, & Assuming these elementary back scatterers are large in number and independent in nature, \\
%**IVM: the above should be 'number' (you had written 'numbers')
14 & Eq 2.1 & $pdf(A_x)=\frac{1}{\sqrt{\pi}\sigma} e^{\frac{A_x^2}{\sigma^2}}$ & $pdf(A_x)=\frac{1}{\sqrt{\pi}\sigma} e^{-\frac{A_x^2}{\sigma^2}}$ \\
%**IVM: did you mention this in the thesis? If so, it might be good to mention.
\end{longtable}    
\rowcolors{1}{white}{}

>>>>

\rowcolors{2}{gray!25}{white}    
\noindent
\begin{longtable}[c]{p{0.08\textwidth}|p{0.08\textwidth}|p{0.36\textwidth}|p{0.36\textwidth}}
\textbf{Page} & \textbf{Line} & \textbf{Gramatical Errors} & \textbf{Corrections} \\
 \hline
\endhead
4 & 5 & missing references & citation added \\
4 & 8 & missing references & citation added \\
5 & 13 & techniques ... has & techniques ... have \\
6 & 5 & many fold & manyfold \\
14 & 5 & Assuming the number of these elementary back scatterers is sufficiently large, & Assuming these elementary back scatterers are large in number and independent in nature, \\
14 & Eq 2.1 & $pdf(A_x)=\frac{1}{\sqrt{\pi}\sigma} e^{\frac{A_x^2}{\sigma^2}}$ & $pdf(A_x)=\frac{1}{\sqrt{\pi}\sigma} e^{-\frac{A_x^2}{\sigma^2}}$ \\
%**IVM: did you mention this in the thesis? If so, it might be good to mention.
\end{longtable}    
\rowcolors{1}{white}{}

### 2014-06-04 answer_thesis_examiner/chap2.tex

\replyToComment
    {Replace the word ``theory'' with ``model'' throughout the thesis}
    {This has been done.}
%**IVM better not use humour... not all examiners have a sense of humour!!    {Search and replace operation done!}

@@

\replyToComment
    {The proposed log-transform model will introduce an inevitable bias error, which may not be able to measure by MSE.}
    {
      It is true. In fact, the thesis does say that log-transformation will introduce bias. %**IVM
      It also shows that MSE evaluation does inherently include a bias evaluation.
      In fact, the thesis argues that MSE evaluation has two components: 1. bias evaluation and 2. variance evaluation, which, for evaluating the performance of SAR speckle filters translates into two criteria: 1. radiometric preservation and 2. noise suppression respectively.
}

@@

\replyToComment
    {Define terms heteroskedastic and homoskedastic in the context of SAR imagery.}
    {Heteroskedastic and homoskedastic are terms defined in a statistical context to respectively denote the fact that different sub-populations of given samples can have different or similar variabilities. In the context of SAR (and POLSAR) imagery they denote the fact that different areas in a given image can have different or similar sample variance.}  %**IVM added the word 'sample'

@@

In general, I wish to express my appreciation towards Examiner No. 2 for his careful, detailed and concise review.
%**IVM: I would skip this-> I am amazed by the fact that the Examiner is able to precisely summarize the long thesis into a single sentence.
I also feel encouraged by the Examiner's suggestion to extract out portions of this thesis as scientific papers for peer review, which has also been taken up and acted upon.

%=====
%
%Examiner No. 2 suggests to further emphasize the significance of the research motivation in \textbf{Section 1.1 and Section 1.2}.
%In a similar fashion, the conclusion chapter should also include the research objectives.
%These have been updated in the revised thesis.
%Even though I would wish to note that the research objectives have been spelled out in the Introduction chapter.
%The examiner also suggested to change the word ``theory'' to ``model''.
%That has also been applied through out the thesis.
%
%\textbf{The second main comment} is to further highlight the novelty claim, which can be splitted into two parts.
%
%\textit{In the first part}, the examiner appears to discount the novelty claim by suggesting that:
% ``the proposed model is derived based on the existing statistical models for SAR and extended to POLSAR''.
%The main approach, in actuality, differs in a subtle but important way:
%The proposed model is derived based on generic mathematical results for multi-dimensional random-walk \cite{Goodman_JOptSocAm_76, Goodman_Springer_1975}.
%These results are well known to be applicable to POLSAR.
%Thus, the derived models by nature are multi-dimensional model.
%However, when collapsed into single-dimension, they match perfectly with existing SAR models.
%As such, the proposed models can be considered as an extension of existing statistical models for SAR.
%
%\textit{In the second part}, the Examiner expresses his doubt in ``the use of MSE (mean squared error) as the single unified evaluation criteria''.
%His main concern: ``the proposed log-transform model will introduce an inevitable bias error''.
%It is no doubt tricky to evaluate evaluation criteria.
%And I can empathize with his feelings.
%Still, I wish to point out that MSE evaluation inherently includes bias evaluation. 
%In fact it has two components: 1. bias evaluation and 2. variance evaluation, which for SAR speckle filter evaluation translates into 1. radiometric preservation and 2. noise suppression respectively.

%( \textbf{ Hai note: }  The Examiner mentions further clarifications to support the claim of novelty in Part II of his report.
%Unfortunately I do not have it at hand.
%It would be great if I can have a look at it!)

%The examiner also suggestion inclusion of several references into \textbf{the literature review} topics of ``relevant SAR/POLSAR speckle filters'' and  ``evaluation of SAR speckle filters''.
%I really appreciate the examiner effort in pointing out specific references.
%They, and some other articles, have been included in the thesis.
%I would like however to seek his empathy towards a couple of points.
%First, a number of the references cited has already been included into the original thesis (e.g \cite{Touzi_2002_TGRS} or \cite{Xie_2002_TGRS}.). 
%Some of them (for example \cite{Argenti_GRSM_2013}) are actually published (Sept 2013) after the submission of the original thesis (Aug 2013).
%Second, please also note that the topics of SAR/POLSAR speckle filters and to some extend, their evaluation, may be considered as part of the thesis's contribution.
%While they do results in published scientific articles, 
%  they are not, however, to be considered as the main contributions of the thesis.
%Rather they serves as application, or demonstration, of the benefits of the thesis's main proposal.
%As such, while I understand the need for comprehensive review, due to various constraint, I seek his understanding that they are probably not to be explored with the same depth and coverage as the main topic of the thesis.

%\textbf{To conclude}, I appreciate the fact that the Examiner is able to a summarize the long thesis into a single sentence.
%Also, portions of this thesis has been extracted out as scientific articles and submitted for peer review.
%Various errata exposed by Examiner No. 2 and have also been updated in the thesis.
%Last but not least, I wish to express my appreciation towards Examiner No.2 for his careful and detailed review.

>>>>

\replyToComment
    {Replace the word ``theory'' with ``model'' throughout the thesis}
    {This has been done.}

@@

\replyToComment
    {The proposed log-transform model will introduce an inevitable bias error, which may not be able to measure by MSE.}
    {
      It is true. In fact, the thesis does say that log-transformation will introduce bias. 
      It also shows that MSE evaluation does inherently include a bias evaluation.
      In fact, the thesis argues that MSE evaluation has two components: 1. bias evaluation and 2. variance evaluation, which, for evaluating the performance of SAR speckle filters translates into two criteria: 1. radiometric preservation and 2. noise suppression respectively.
}

@@

\replyToComment
    {Define terms heteroskedastic and homoskedastic in the context of SAR imagery.}
    {Heteroskedastic and homoskedastic are terms defined in a statistical context to respectively denote the fact that different sub-populations of given samples can have different or similar variabilities. In the context of SAR (and POLSAR) imagery they denote the fact that different areas in a given image can have different or similar sample variance.}

@@

In general, I wish to express my appreciation towards Examiner No. 2 for his careful, detailed and concise review.
I also feel encouraged by the Examiner's suggestion to extract out portions of this thesis as scientific papers for peer review, which has also been taken up and acted upon.
